### 2014-07-09 tex/proofs.tex
Clarified definitions for homomorphism and representation, and the field access lemma statement

\begin{definition}
A \textbf{heap homomorphism} $(g\ h)$ between two states $s_x$ and $s_y$ is defined as a pair of functions $g:\cfgnt{r} \mapsto \cfgnt{r}$ and $h:\cfgnt{l} \mapsto \cfgnt{l}$ such that for any reference $r \in \mathit{refs}(s_x)$, location $l \in \mathit{locs}(s_x)$, and field $f$, $$ (\phi_x\ l) \in \cfgnt{L}_x(r) \Rightarrow (\phi_y\ h(l))\in \cfgnt{L}_y(g(r))$$ and $$ r = \cfgnt{R}_x(l,f) \Rightarrow g(r) = \cfgnt{R}_y(h(l),f)$$ If a such a pair of functions exists from one state $s_x$ to another state $s_y$ we say that state $s_x$ is \textbf{heap homomorphic} to state $s_y$, indicated by the notation $s_x \rightharpoonup_{(g\ h)} s_y$.

Suppose we take the set of constraints from the image of $s_x$ in $s_y$ under $(g\ h)$ :
$$\chi = \{ \phi\ | \exists (r \in \cfgnt{R}_x,\  l \in \cfgnt{L}_x) ( (\phi\ h(l)) \in \cfgnt{L}_y (g(r))  \}$$ and we conjoin those constraints with the global invariant $\phi_y$ from $s_y$ :
$$\phi_G = \phi_y \wedge (\bigwedge_{\phi_i \in \chi} \phi_i) $$
 If the expression $\phi_G$ is satisfiable, we say that the heap homomorphism $s_x \rightharpoonup_{(g\ h)} s_y$ is \textbf{valid}.
\end{definition}
\begin{definition}
\label{representation}
The \textbf{representation relation} is defined as follows: given two states $s_\ell$ and $s_s$, $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a valid heap homomorphism $\ s_\ell \rightharpoonup_{(g\ h)} s_s $. The expression $s_\ell \sqsubset s_s $ can be read as "state $s_\ell$ is represented by state $s_s$ . 
\end{definition}

\begin{definition}
\label{congruent}
A state $s$ is \textbf{congruent} to a set of states $\mathcal{S}$ if and only if $s$ represents every state in $\mathcal{S}$ and represents no other state: 
$$s \cong \mathcal{S} : s_i \in \mathcal{S} \Leftrightarrow s_i \sqsubset s $$
\end{definition}

Need to define a \emph{lazy state} and a \emph{summary state} (or whatever name we are using).

@@

\begin{lemma}
If symbolic state $s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$ is exact with respect to some initial state $s_0$ and control flow path $\pi_n$, then the state $s_s^\prime : s_s \rightarrow_s s_f$ is exact with respect to $s_0$ and $\pi_{n+1}$.
\end{lemma}

@@

Case 1: suppose all of the pertinent fields in $s_s$ are initialized. Take an arbitrary lazy state $s_\ell \sqsubset s_s$. Since $s_s$ is exact,  $s_\ell = \lp \cfgnt{L}_{\ell}\ \cfgnt{R}_{\ell}\ \phi_L\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k} \rp \rp$, and that $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$. If we apply the state transition functions to achieve states $s_\ell^\prime : s_\ell \rightarrow_\ell s_\ell^\prime$ and $s_s^\prime : s_s \rightarrow_s s_s^\prime$, we find that:
$$s_\ell^\prime = \lp \cfgnt{L}_{\ell} [\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}_{\ell}\ \phi_L\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$
 and 
 $$ s_s^\prime = \lp \cfgnt{L}_{s}[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}_{\mathcal{S}},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$

We now show that $s_\ell^\prime \sqsubset s_s^\prime$. Since $\eta$, $e$, and $k$ are identical between $s_s^\prime$ and $s_\ell^\prime $, the first condition is met by default. Now we construct functions $g^\prime : g^\prime = g[ r^\prime \mapsto r^\prime]$ and $h^\prime : h^\prime = h$. Observe that since $s_\ell \rightarrow s_s$, and since $\cfgnt{R}_\ell$ and $\cfgnt{R}_s$ are unchanged from states $s_\ell$ to $s_\ell^\prime$ and $s_s$ to $s_s^\prime$ respectively, we are guaranteed that $ r = \cfgnt{R}_\ell(l,f) \Rightarrow g^\prime(r) = \cfgnt{R}_s(h^\prime(l),f)$. Since $(\phi_\ell^\prime\ l^\prime) =  \cfgnt{L}_\ell(\cfgnt{R}_\ell(l,f))$, and since $(g\ h)$ is valid, we know that:
 $$(\phi_s \wedge \phi_s^\prime\ l^\prime) \in \mathbb{VS}\lp \cfgnt{L}_{\mathcal{S}},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp$$ 
From this, we may deduce that:
$$ (\phi_\ell\ l) \in \cfgnt{L}_\ell^\prime(r^\prime) \Rightarrow (\phi_s \wedge \phi_s^\prime\ h^\prime(l))\in \cfgnt{L}_s^\prime(g^\prime(r^\prime))$$
Since $r^\prime$ the only new addition to $L_\ell^\prime$ and $L_s^\prime$, we now know that the assertion above holds for all $l \in s_\ell^\prime$. Thus, we have shown that $(g^\prime\ h^\prime)$ is a heap homomorphism from $s_\ell^\prime$ to $s_s^\prime$. Furthermore, since $\mathbb{S}(\phi_s\wedge\phi_s^\prime\wedge \phi_g)$ holds true, we know that $(g^\prime\ h^\prime):\ s_\ell^\prime \rightarrow s_s^\prime$ is valid. Since there is a valid heap homomorphism, and since $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, we  by definition \ref{representation} know $s_\ell^\prime \sqsubset s_s^\prime$. We have now shown that for any lazy state $s_\ell$: 
$$s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime$$

@@

Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$, but $s_i^\prime \notin \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$. Since $s_i^\prime \sqsubset s_s^\prime$, there must exist a valid homomorphism $(g_i^\prime h_i^\prime): s_i^\prime \rightarrow s_s^\prime$. If $(g_i^\prime\ h_i^\prime)$ is valid, then there must also exist a valid homomorphism $(g_i\ h_i) : s_i \rightarrow s_s$, and by extension, state $s_i \sqsubset s_s$. However, since $s_s$ is exact, $s_i \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n})$, and by our previous result, $s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$. We have a contradiction. Therefore, $$s_i^\prime \sqsubset s_s^\prime \Rightarrow s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$$ Combining the two previous equations, we find that 
$$s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime)$$
By definition \ref{congruent}, $s_s^\prime \equiv \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, and so by definition \ref{exact}, $s_s^\prime$ is exact.

>>>>

\begin{definition}
A \textbf{homomorphism} $s_x \rightharpoonup_{(g\ h)} s_y$, from state $s_x = ( \cfgnt{L}_x\ \cfgnt{R}_x\ \phi_x\ \eta_x\ \cfgnt{e}_x\ \cfgnt{k}_x )$ to state $s_y = ( \cfgnt{L}_y\ \cfgnt{R}_y\ \phi_y\ \eta_y\ \cfgnt{e}_y\ \cfgnt{k}_y )$, is defined as follows: 
%a pair of functions $g:\mathcal{R} \mapsto \mathcal{R}$ and $h: \mathcal{L} \mapsto \mathcal{L}$ such that the following conditions are met:

\begin{array}{l}
 s_x \rightharpoonup_{(g\ h)} s_y \Leftrightarrow \\
\ \ \ \ \ \ \ \ \exists g:\mathcal{R} \mapsto \mathcal{R}\ ( \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{r} \in \mathcal{R}\ (\forall \cfgnt{l} \in \mathcal{L}\ ( \\ 
\ \ \ \ \ \ \ \ \ \ \ \ (\phi_x\ \cfgnt{l}) \in \cfgnt{L}_x(\cfgnt{r}) \Rightarrow (\phi_y\ h(\cfgnt{l}))\in \cfgnt{L}_y(g(\cfgnt{r}))\ \wedge \\
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \cfgnt{r} = \cfgnt{R}_x(\cfgnt{l},f) \Rightarrow g(\cfgnt{r}) = \cfgnt{R}_y(h(\cfgnt{l}),f) )) )) 
\end{array}

\begin{definition}
\label{representation}
The \textbf{representation relation} is defined as follows: given lazy state $s_\ell$ and summary state $s_s$, $s_\ell \sqsubset s_s $ if and only if $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, and there exists a homomorphism $\ s_\ell \rightharpoonup_{(g\ h)} s_s $ such that if $$\chi = \{ \phi\ | \exists (r \in \cfgnt{R}_x,\  l \in \cfgnt{L}_x) ( (\phi\ h(l)) \in \cfgnt{L}_y (g(r))  \}$$ then 
\begin{equation}
\label{eqn:valid}
 \mathbb{S}( \phi_y \wedge (\bigwedge_{\phi_i \in \chi} \phi_i)) 
\end{equation}
\end{definition}

\begin{definition}
\label{congruent}
A summary state $s$ is \textbf{congruent} to a set of lazy states $P$ if and only if $s$ represents every state in $P$ and represents no other state: 
$$s \cong P \Leftrightarrow \forall s_i \in \mathcal{S}\ (s_i \in P \Leftrightarrow s_i \sqsubset s) $$
\end{definition}

@@

%we need to define how r' is arrived at for this one to work...
\begin{lemma}
If there are symbolic states $s_s$ and $s_s^\prime$, control sequences $\pi_n$ and $\pi_{n+1}$, initial state $s_0$, and reference $\cfgnt{r}^\prime$ such that the following conditions hold:
\begin{align}
s_s &= \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp \\
s_s &\cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp \\
\cfgnt{r}^\prime &= \mathrm{fresh}_r\lp \rp \\
\pi_{n+1} &=\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp \\
s_s &\rightarrow_s s_s^\prime
\end{align}
%$$s_s = \lp \cfgnt{L}_{\mathcal{S}}\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}\rp \rp$$ 
%$$s_s \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_n\rp$$ 
%$$\pi_{n+1} =\pi_n\ \lp \eta\ \cfgnt{r}^\prime\ \cfgnt{k} \rp$$

then 
$$s_s^\prime \cong \mathbb{FS}\lp \rightarrow_{\phi},s_0,\pi_{n+1} \rp$$
\end{lemma}

@@

Case 1: suppose all of the pertinent fields in $s_s$ are initialized. Take an arbitrary lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$. Since $s_s$ is exact,  $s_\ell = \lp \cfgnt{L}_{\ell}\ \cfgnt{R}_{\ell}\ \phi_\ell\ \eta\ \cfgnt{r}\ \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k} \rp \rp$, and $s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$. If we apply the state transition functions to achieve states $s_\ell^\prime$ and $s_s^\prime$ such that $s_\ell \rightarrow_\ell s_\ell^\prime$ and  $s_s \rightarrow_s s_s^\prime$, we find that:
$$s_\ell^\prime = \lp \cfgnt{L}_{\ell} [\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}_{\ell}\ \phi_L\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$
 and 
 $$ s_s^\prime = \lp \cfgnt{L}_{s}[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}_{\mathcal{S}},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}_{\mathcal{S}}\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp $$

We now show that $s_\ell^\prime \sqsubset s_s^\prime$. Since $\eta$, $e$, and $k$ are identical between $s_s^\prime$ and $s_\ell^\prime $, the first condition is met by default. Now we construct functions $g^\prime$ and $h^\prime$ such that $g^\prime = g[ r^\prime \mapsto r^\prime]$ and $h^\prime = h$. Observe that since $s_\ell \rightharpoonup_{(g\ h)} s_s$, and since $\cfgnt{R}_\ell$ and $\cfgnt{R}_s$ are unchanged from states $s_\ell$ to $s_\ell^\prime$ and $s_s$ to $s_s^\prime$ respectively, we are guaranteed that $ r = \cfgnt{R}_\ell(l,f) \Rightarrow g^\prime(r) = \cfgnt{R}_s(h^\prime(l),f)$. Since $(\phi_\ell^\prime\ l^\prime) =  \cfgnt{L}_\ell(\cfgnt{R}_\ell(l,f))$, and since $(g\ h)$ is valid, we know that:
 $$(\phi_s \wedge \phi_s^\prime\ l^\prime) \in \mathbb{VS}\lp \cfgnt{L}_{\mathcal{S}},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp$$ 
From this, we may deduce that:
$$ (\phi_\ell\ l) \in \cfgnt{L}_\ell^\prime(r^\prime) \Rightarrow (\phi_s \wedge \phi_s^\prime\ h^\prime(l))\in \cfgnt{L}_s^\prime(g^\prime(r^\prime))$$
Since $r^\prime$ the only new addition to $L_\ell^\prime$ and $L_s^\prime$, we now know that the assertion above holds for all $l \in \mathcal{L}$. Thus, we have shown that $s_\ell^\prime \rightharpoonup_{(g\ h)} s_s^\prime$. Furthermore, since $\mathbb{S}(\phi_s\wedge\phi_s^\prime\wedge \phi_g)$ evaluates to $\cfgt{true}$, we know that equation \ref{eqn:valid} also evaluates to $\cfgt{true}$. Since there is a valid heap homomorphism, and since $\eta_{\ell} = \eta_{s} ,\ \cfgnt{e}_{\ell} = \cfgnt{e}_{s} ,\ \cfgnt{k}_{\ell} = \cfgnt{k}_{s}$, we  by definition \ref{representation} know $s_\ell^\prime \sqsubset s_s^\prime$. We have now shown that for any lazy state $s_\ell$: 
$$s_\ell \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Rightarrow s_\ell^\prime \sqsubset s_s^\prime$$

@@

Now, suppose that there exists a state $s_i^\prime$ such that $s_i^\prime \sqsubset s_s^\prime$, but $s_i^\prime \notin \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$. Since $s_i^\prime \sqsubset s_s^\prime$, there must exist a valid homomorphism $s_i^\prime \rightharpoonup_{(g^\prime\ h^\prime)} s_s^\prime$. If $(g_i^\prime\ h_i^\prime)$ is valid, then there must also exist a valid homomorphism $(g_i\ h_i) : s_i \rightarrow s_s$, and by extension, state $s_i \sqsubset s_s$. However, since $s_s$ is exact, $s_i \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n})$, and by our previous result, $s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$. We have a contradiction. Therefore, $$s_i^\prime \sqsubset s_s^\prime \Rightarrow s_i^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_{n+1})$$ Combining the two previous equations, we find that 
$$s_\ell^\prime \in \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n) \Leftrightarrow s_\ell^\prime \sqsubset s_s^\prime)$$
By definition \ref{congruent}, $s_s^\prime \equiv \mathbb{FS}(\rightarrow_{\ell},s_0,\pi_n)$, and so by definition \ref{exact}, $s_s^\prime$ is exact.
